THESIS PROJECT PROPOSAL

### 2019-11-11 project_ashish/paper2.tex
Rename paper.tex to paper2.tex

@@

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/pg.png}
  \caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
   \label{figure 2}
\end{figure}

@@

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cd7.png}
  \caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
   \label{figure 3}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms5.png}
  \caption{Standard model Higgs boson production in association with top quark and top anti-quark, top quark decaying to W boson and bottom quark and  W boson decaying to leptons.}
   \label{figure 4}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms13.png}
  \caption{Scan of $−2Δln(L)$ versus $κ_t$ for the data (black line) and the individual channels (blue, red, and green), compared to Asimov data sets corresponding to the SM expectations (dashed lines).}
   \label{figure 5}
\end{figure}

@@

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms12.png}
  \caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
   \label{figure 6}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/lum6.png}
  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities. Points
show instant brightness while the line shows brightness accumulated.}
   \label{figure 7}
\end{figure}

@@

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/tq.png}
  \caption{Higgs production using the top quark (left) and W boson (right).}
  \label{figure 8}

  \begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cms.png}
  \caption{Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
   \label{figure 9}
\end{figure}

@@

>>>>

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms12.png}
  \caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
   \label{figure 2}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/pg.png}
  \caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
   \label{figure 3}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/tq.png}
  \caption{Higgs production using the top quark (left) and W boson (right).}
   \label{figure 4}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cd7.png}
  \caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
   \label{figure 5}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/lum6.png}
  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities. Points
show instant brightness while the line shows brightness accumulated.}
   \label{figure 6}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cms.png}
  \caption{\onehalfspacing Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
   \label{figure 7}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms5.png}
  \caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quark decaying to W boson and bottom quark and  W boson decaying to leptons.}
   \label{figure 8}
\end{figure}

Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. 
These had eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was 
discovered in 1995 in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass 
energy of 1.8 TeV untill 2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 
colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years. The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC) located at CERN. It is designed to detect particles known as muons very accurately. The CMS detector has the form of a cylindrical onion, with several concentric layers of components. Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to bend them in opposite directions and measure your momentum. A silicon tracker, made of about 75 
million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles bent with very high precision \cite{Chatrchyan:2008aa}. The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid as shown in Figure 2. In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV. So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the standard model (SM). LHC during the first run in 2011 and 2012 reached a peak luminosity of 7.7 \times 10^{33} $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS. The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles. In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  placein parallel during one shutdown, at around 2023-25 (Long shutdown 3), with some of the modification anticipated in 2019-2020 (LS2). This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ in 10-12 years. All the hadron colliders in the world have so far produced a total integrated luminosity of about 10 $fb^{-1}$, while the LHC will deliver about 300 $fb^{-1}$ in its first 10-12 years of life \cite{collaborations2019report}. LHC will reach an integrated luminosity of about 300 $fb^{-1}$ by 2023 as shown in Figure 6. \\

@@

@@

@@

@@

@@

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cms13.png}
  \caption{Lowest order Feynman diagrams for s-channel tH production.}
   \label{figure 20}
\end{figure}
